---
title: "Global climate heading in a Wrong Direction: Mechanism behind the occurrence of climatic change and analysis of Children Climate risk index"
author: "Victor & Floriann"
format: 
  html:
    toc: true                   # This creates the table of context menu
    toc-depth: 2                # Increase if you want to have subsections in the table of context menu
    number-sections: true
    code-fold: true
    code-tools: true
bibliography: references.bib
---

```{r}
#| label: packages
#| message: false

# These are the packages used in the report
# Import required package

library(tidyverse)
library(dplyr)
library(magrittr)
library(ggplot2)
library(plotly)
library("RColorBrewer")
library(skimr)
library("zoo")
library(plotly) #world map
library(ggridges)
library(forcats)
options(warn=-1)
library(reshape2)
library(gganimate)
library("gridExtra")
library("ggpubr")
library(gganimate)
require(plyr)
library(rnoaa)
library(ggthemes)
library(lubridate)
library(rgdal)
```

This slide deck presents the main insights:

```{=html}
<iframe class="slide-deck" style="border:1px solid lightgray;" width="100%" height="500" src="presentation.html"></iframe>
```

[Presentation in standalone browser tab.](presentation.html){.internal target="_blank"}

Detailed project report

## Executive Summary

## Introduction
<p align='justify'>
*Climate Science* has become an intimidating subject matter which is drawing attention in recent days.
It is evident that human activities are driving the global warming since mid-20th century. The industrial activities that our modern civilization has taken up leads to raised atmospheric carbon dioxide levels.
</p>
<p align='justify'>
UN Climate change states that the past seven years were the warmest on record. Countries that host billions of people and are responsible for up to 70% of human-caused emissions are predicted to get affected the most. This leads to increasing socio-economic impacts. Consequently, making populations vulnerable to extreme weather in different parts of the world. 
</p>
<p align='justify'>
Climate impacts heading into uncharted territory of destruction by increasingly devastating and leading to many natural calamities. This report will unveil the most inquisitive questions arising which causes and mechanism in global warming along with the human activities leading to natural changes in the environment.  As a consequence how humankind is affected, especially children. This study will address the following questions,
</p>
<p align='justify'>
1. What is the mechanism behind the occurrence of climatic change?
	- Emissions of greenhouse gases over a period of time due to industrial revolution.
	- Descriptive statistics on factor facilitating Climate change.
2. Study the trend in natural disaster due to global warming.
3. Analysis on children vulnerability to climatic change with respective to Children Climate risk index(CCRI) data.
</p>

## Data Source

<br>
The Key metrics which contributes to the global climate change is maintained by Our World in Data. 
Data source will be accessed by from Github API with *R* language. There are 3 datasets which will be used for this study, namely
<br>
1. Emission levels data and temperature<br>
	  Link : *<https://github.com/owid/co2-data>* <br>
2. Natural disaster data<br>
	  Link : *<https://github.com/owid/owid-datasets/tree/master/datasets/Natural%20disasters%20(EMDAT%20–%20decadal)>* <br>
3. Global temperature data<br>
    Link : *<https://data.giss.nasa.gov/gistemp/ https://data.giss.nasa.gov/gistemp/tabledata_v4/T_AIRS/GLB.Ts+dSST.csv>* <br>
4. Children’s Climate and Environment Risk Index<br>
    Link : *<https://sdmx.data.unicef.org/webservice/data.html>*

```{r}
#Extracting data:
climate_change <- read.csv(file = "data/climate_change.csv",TRUE, sep = ",", stringsAsFactors = FALSE)
cceri_data <- read.csv(file = "data/CC_ERI.csv",TRUE, sep = ",", stringsAsFactors = FALSE)
natural_disaster_data <- read.csv(file = "data/natural_disaster.csv",TRUE, sep = ",", stringsAsFactors = FALSE)
continent <- read.csv(file = "data/Continents.csv",TRUE, sep = ",", stringsAsFactors = FALSE)

#Statistical description
#dim(climate_change)
#dim(cceri_data)
#dim(natural_disaster_data)

##Summary statistics with SKIM function
#skim(climate_change)
#skim(cceri_data)
#skim(natural_disaster_data)

##Checking NA values in the dataset
#apply(is.na(climate_change),2, sum)
#apply(is.na(cceri_data),2, sum)
#apply(is.na(natural_disaster_data),2, sum)
```

## Visualisations

### Global surface temperature

#### Global surface temperature rise

```{r message=FALSE}
#### Visual 1: adding Year-Month variable as year_date
climate_change$year <- as.yearmon(paste(climate_change$Year, climate_change$Month), "%Y %m")

# plotting Temperature-Year 
ggplot(climate_change, aes(year, Temp)) + 
  geom_line(aes(color = "actual temperature")) +
  geom_smooth(aes(se=FALSE, color = "Avg temp")) +
  labs(title = "Global Temperature is rising",
       subtitle = "Global temperature rise from 1985 to 2022 (°C)",
       y = "Global Earth Temperature",
       color = "Temperature",
       caption = "Annual estimates of mean surface temperature change measured in Degree Celsius for World.",) +
  scale_colour_manual(values = c("orange", "blue"),
                      labels = c("Actual temperature", "Average temperature")) +
  theme_classic() +
  scale_y_continuous(limits = c(-.5,1.5)) +
  scale_x_continuous(limits = c(1985,2022)) +
  theme(plot.title = element_text(face = "bold",
                                  margin = margin(10, 0, 10, 0),
                                  size = 14)) +
  theme(panel.grid.minor = element_blank()) 
```

<p align='justify'>

Air temperatures on Earth have been rising since the Industrial Revolution. According to an ongoing temperature analysis led by scientists at NASA’s Goddard Institute for Space Studies (GISS), the average global temperature on Earth has increased by at least 1.1° Celsius (1.9° Fahrenheit) since 1880. A one-degree global change is significant because it takes a vast amount of heat to warm all of the oceans, the atmosphere, and the land masses by that much. In the past, a one- to two-degree drop was all it took to plunge the Earth into the Little Ice Age. A five-degree drop was enough to bury a large part of North America under a towering mass of ice 20,000 years ago.

As seen from the line chart above,the global temperature has been increasing since 1990, with the 2010–2019 decade being the warmest on record. The hottest year on record was 2016, and it was followed by 2019 and 2020. In the Arctic, where temperatures have risen at a rate that is roughly twice as fast as the world average, the warming trend has been particularly noticeable.

The Earth's climate has been greatly impacted by this warming trend, which has led to more frequent and severe heatwaves, droughts, and extreme weather events like storms and floods. Additionally, it has aided in the glacier and polar ice cap melting that is raising sea levels.

</p>

#### Global Temperature density

```{r fig.height = 6, message=FALSE}
#Visual 2: Temperature density

# adding right and left hand sided labels
climate_change <- climate_change %>%
  mutate(label_rt = if_else(Month == 12 & Year%%2 == 0, 
                            as.character(Year), NA_character_)) %>%
  mutate(label_lt = if_else(Month == 1 & Year%%2 != 0, 
                            as.character(Year), NA_character_))

ggplot(climate_change, aes(x = Temp, y = as.factor(Year))) + 
  geom_density_ridges_gradient(aes(fill = ..x..), 
                               scale = 3, size = 0.3, alpha = 0.5) +
  geom_vline(xintercept = 0.5, alpha = 0.5, color = "red", linetype = "dotted")+
  scale_fill_gradientn(colours = c("#87CEFA", "#FFFFE0", "#FF0000"),
                       name = "Temperature (°C)") +
  labs(title = 'Shifting Distribution of Earth Temperature',
       subtitle = "Temperature Difference in degrees Celsius from the year 1983 to 2022",
       caption = "NASA: https://svs.gsfc.nasa.gov/4891",) + 
  theme(plot.title = element_text(face = "bold",
                                  margin = margin(10, 0, 10, 0),
                                  size = 14)) +
  theme(legend.position = c(0.8,0.2)) +
  xlab("Temperature") + 
  ylab("Year") + 
  theme_classic()

```

<p align='justify'>

This visualization shows how the distribution of land temperature anomalies has varied over time. As the planet has warmed, we see the peak of the distribution shifting to the right. The distribution of temperatures broadens as well. 

This broadening is most likely due to differential regional warming rather than increased temperature variability at any given location.We can see extreme values since 2000, but after 2009 it has become significant.

</p>

### Sea level change due to climate change

#### North pole Sea level

```{r message=FALSE}
# North pole Sea level
north_sea <- sea_ice(year = 2017:2022, month = 'May', pole = "N")
names(north_sea) <- seq(2017, 2022, 1)
df_north <- ldply(north_sea)

ggplot(df_north, aes(long, lat, group = group)) +
  geom_polygon(fill = "steelblue") +
  ggtitle("Changes in Sea Ice Level for North pole") +
  theme_ice() +
  facet_wrap(~.id)
```

<p align='justify'>

Changes in the amount of sea ice can disrupt normal ocean circulation, thereby leading to changes in global climate.  Even a small increase in temperature can lead to greater warming over time, making the polar regions the most sensitive areas to climate change on Earth.

The Arctic Ocean is covered in layers of frozen seawater. Each winter, this sea ice increases significantly, usually reaching its peak in March. Every summer, it melts just as dramatically, reaching its lowest point in September. Although there has been a natural variation for thousands of years, recent decades have seen a decline in winter and summer trends.

The visualizations show the warmer water rise overtime due to thermal expansion and dissolves floating ice shelves. The Polar Regions are under severe risk because of the enormous sizes of the Antarctic and Greenlandic ice sheets.

</p>

#### South Pole Sea Ice Level

```{r message=FALSE}
#### South Pole Sea Ice Level

south_sea <- sea_ice(year = 2017:2022, month = 'May', pole = "S")
names(south_sea) <- seq(2017, 2022, 1)
df_south <- ldply(south_sea)

# Plot data
ggplot(df_south, aes(long, lat, group = group)) + 
  geom_polygon(fill = "steelblue") + 
  ggtitle("Changes in Sea Ice Level for South pole") + 
  theme_ice() + 
  facet_wrap(~.id)

```

<p align='justify'>

While Arctic sea ice is melting at an unprecedented rate, Antarctic sea ice is moving in the opposite direction.

This is due to the fact that icy winds blowing off Antarctica, as well as a powerful ocean current that circles the frozen continent, are far more important factors in the formation and persistence of Antarctic sea ice than temperature changes.

The powerful Southern Ocean Circumpolar Current keeps warmer ocean water from reaching the Antarctic sea ice zone, aiding in the continent's isolation. The winds within that ice zone keep the water extremely cold, allowing the sea ice cover to grow in recent years despite significant global warming.

</p>

#### Sea Ice Level changes comparision

```{r message=FALSE}

north_data <- read.csv(url("https://www.ncdc.noaa.gov/snow-and-ice/extent/sea-ice/N/8.csv"),skip=3)
south_data = read.csv(url("https://www.ncdc.noaa.gov/snow-and-ice/extent/sea-ice/S/8.csv"),skip=3)

north_data$'North Sea Ice Level' = north_data$Anomaly
south_data$'South Sea Ice Level' = south_data$Anomaly

poles_data = merge(north_data[,-c(2,3)], south_data[,-c(2,3)], by="Date")

poles_Melted <- reshape2::melt(poles_data, id.var='Date')

ggplot(poles_Melted, aes(x=Date, y=value, col=variable)) + 
  geom_line(linetype="solid", size=1) +
  xlab("Year") +
  ylab("Change is Sea Ice Level") +
  ggtitle("Comparing Changes in Sea Ice Level") +
  theme_classic()
```

<p align='justify'>

The Northern Hemisphere experiences the most seasonal change in the amount of ice and snow cover. Put white caps on the top and bottom of the Earth. The bottom cap merely doubles from summer to winter, whereas the top cap grows by a factor of six. The snow cover is to cause for this variation.

Snow cover on land in the Northern Hemisphere ranges from less than 2 million km2 in the summer to 40 to 50 million km2 in the winter. The Southern Hemisphere has little snow cover. Land ice covers approximately 14 million km2 of Antarctica year round, with little variation from summer to winter. The extent of sea ice in the Arctic varies seasonally between 7 and 15 million km2, whereas the extent of sea ice in the Antarctic varies much more - from around 3 million km2 in summer to 18 million km2 in winter. This means that the Antarctic has less multi-year sea ice than the Arctic, where much of the sea ice is older than one year.

From the graph, the changes in Northern Sea ice level is consistently decreasing over the years, whereas the Southern sea ice level is consistently increasing.

</p>

### Multivariate El Nino Southern Oscillation index by Year

<p align='justify'>

The El Nino Southern Oscillation (ENSO) is the primary predictor of global climate disruptions. It is a naturally occurring anomalous state of tropical Pacific coupled ocean-atmosphere conditions. These can last for several seasons and have serious regional consequences.

The Multivariate ENSO Index (MEI) is used to track ENSO. It consists of six major variables observed over the tropical Pacific. These six variables are as follows: sea-level pressure (P), surface wind zonal (U) and meridional (V) components, sea surface temperature (S), surface air temperature (A), and total cloudiness fraction of the sky (C).

</p>

```{r message=FALSE}
climate_change <- climate_change %>% mutate(year_month = ymd(paste(climate_change$Year, climate_change$Month, truncated = 1))) 

climate_change %>%
  arrange(year_month) %>%
  ggplot() + 
  geom_line(aes(year_month, MEI, color = MEI), size = 1) +
  scale_color_gradient2(low = 'blue', high = 'red') + 
  labs(title = "Multivariate El Nino Southern Oscillation index by Year", 
       caption = "Source: ESRL/NOAA Physical Sciences Division") + 
  xlab("Year") +
  ylab("MEI") + 
  theme(plot.title = element_text(hjust = 0.5)) +
  theme_minimal()
```

<p align='justify'>

</p>

### The Green House Effect

<p align='justify'>

The greenhouse effect is the primary cause of climate change. Some gases in the Earth's atmosphere act like greenhouse glass, trapping the sun's heat and preventing it from escaping into space and causing global warming.

Many of these greenhouse gases are naturally occurring, but human activities are increasing their concentrations in the atmosphere, particularly:carbon dioxide (CO2), methane,and nitrous oxide.

Other greenhouse gases are emitted by human activities in smaller quantities. Methane is a more powerful greenhouse gas than CO2, but has a shorter atmospheric lifetime. Nitrous oxide, like CO2, is a long-lived greenhouse gas that accumulates in the atmosphere over decades to centuries. 

</p>

#### Carbon Dioxide level changes

```{r message=FALSE}
climate_change_chart <- ggplot(climate_change, aes(x = Year, y = Temp, fill = CO2)) + 
  xlab("Year") +
  ylab("Temperature") +
  theme_minimal(base_size = 14)

barplot <- climate_change_chart +
  geom_bar( position = "dodge", stat = "identity",color= "white")
ggplotly(barplot)

```

<p align='justify'>

Since the beginning of the industrial revolution, the carbon dioxide emissions produced by industrial operations and the global burning of fossil fuels have dramatically increased at a constant rapid rate. Emissions of carbon dioxide (CO2) increased rapidly starting in the 1950s and peaked in 2000 at 25.23 billion tons. Between 2000 and 2010, emissions increased by 32 percent.

</p>

#### Vartations of CO_2, N2O, CH4 and MEI by year

```{r message=FALSE}
climate_change_ymd <- climate_change %>%
  mutate(year_month = ymd(paste(climate_change$Year, climate_change$Month, truncated = 1))) 

scat_plot1 <-  ggplot(climate_change_ymd, aes(year_month, CO2))+geom_line(colour="blueviolet")+geom_smooth(method = "lm")+ggtitle("Carbon Dioxide") + theme_minimal(base_size = 14)
scat_plot2<-  ggplot(climate_change_ymd, aes(year_month, N2O))+geom_line()+geom_smooth(method = "lm")+ggtitle("Nitrous Oxide") + theme_minimal(base_size = 14)
scat_plot3<-  ggplot(climate_change_ymd, aes(year_month, CH4))+geom_line(colour="springgreen4")+geom_smooth(method = "lm")+ggtitle("Methane") + theme_minimal(base_size = 14)
scat_plot4 <-  ggplot(climate_change_ymd, aes(year_month, MEI))+geom_line(colour="mediumorchid4")+ggtitle("MEI") + theme_minimal(base_size = 14)
grapgh_arrange<-ggarrange(scat_plot1, scat_plot2, scat_plot3, scat_plot4 + rremove("x.text"), 
          labels = c("A", "B", "C", "D"),
          ncol = 2, nrow = 2)
annotate_figure(grapgh_arrange,
                top = text_grob("Vartations of CO_2, N2O, CH4 and MEI by year", color = "red", face = "bold", size = 14)
)

```

CO2:
<p align='justify'>

This line graph depicts the monthly average carbon dioxide measurements in parts per million (ppm) since 1990. Summertime growth and winter decay of Northern Hemisphere vegetation drive the seasonal cycle of highs and lows (small peaks and valleys). Human activities are driving the long-term trend of rising CO2 levels.

From the line graph, the CO2 emissions has been on a rapid increase from 1990 at about 355ppm to about 387ppm in 2010. The red line signifies the global average co2 emissions concentration. An increase in greenhouse gas concentrations in the atmosphere causes positive climate forcing, or warming. 

According to the Global Carbon Update 2021, annual emissions from burning fossil fuels have increased every decade since the mid-twentieth century, from an average of 3 billion tons of carbon (11 billion tons of carbon dioxide) per year in the 1960s to 9.5 billion tons of carbon (35 billion tons of carbon dioxide) per year in the 2010s. The total warming effect of greenhouse gases added to the Earth's atmosphere by humans increased by 45 percent between 1990 and 2019. The warming effect caused by carbon dioxide alone increased by 36%.

</p>

Methane:

<p align='justify'>
This graph shows the increase of methane gas over the years. There was a whopping 145ppb increase between 1980 and 2000. From year 2000,the rate of methane gas slowed down and become relatively constant between 2005 and 2010.
</p>

Nitrous Oxide:

<p align='justify'>
Nitrous oxide is a greenhouse gas that is over 300 times as potent as CO2 and also destroys the ozone layer in the stratosphere. According to a new study published in Nature, nitrous oxide emissions from human activities have increased by 30% since 1980, which is a faster increase than experts had initially predicted.The graph shows a rapid growth of nitrous oxide emissions since 1980 till 2010.
</p>

### Natural disaster due to climate changes

<p align='justify'>
Climate change can increase disaster risk in a variety of ways - by altering the frequency and intensity of hazard events, affecting vulnerability to hazards, and changing exposure patterns.

The next visualizations would show how climate change has contributed to several natural disasters and its effects on people.
</p>

```{r message=FALSE}
##Pre-processing
#Selecting only required columns from Natural disaster data for further analysis and visualization
disaster_data <- natural_disaster_data %>% 
                  select(Entity,Year, affected_all_disasters, affected_temperature, affected_flood, affected_wildfire, 
                         deaths_all_disasters, deaths_temperature, deaths_flood, deaths_wildfire,
                         homeless_all_disasters, homeless_temperature, homeless_flood, homeless_wildfire,
                         injured_all_disasters, injured_temperature, injured_flood, injured_wildfire,
                         total_affected_all_disasters, total_affected_temperature, total_affected_flood, total_affected_wildfire,total_damages_pct_gdp_all_disasters, total_damages_pct_gdp_temperature, total_damages_pct_gdp_flood, total_damages_pct_gdp_wildfire) %>%
                  group_by(Entity) %>% filter(Year == max(Year)) %>% # Take the most recent date per country
                  group_by() %>% #removing groupby
                  drop_na() 

#Selecting only continents from the dataset:
# Asia, Africa, North America, South America, Antarctica, Europe, and Australia.
continent_data <- filter(disaster_data, 
                         Entity %in% c("Asia", "Africa", "North America", "South America", "Antarctica",
                                     "Europe", "Australia"))

continent_data_new <- continent %>% 
              select(name,alpha.3,region,sub.region) %>%
              drop_na()

#Joining disaster data with continent data:
colnames(continent_data_new)[1] <- "Entity"
disaster_data_country <- left_join(disaster_data, continent_data_new, by = c('Entity'))
disaster_data_country <- disaster_data_country %>% 
                        drop_na() 
```

#### People affected due to all disaster in all continents

```{r message=FALSE}
# affected_all_disasters
continent_data$affected_all_disasters= 100*(continent_data$affected_all_disasters/sum(continent_data$affected_all_disasters))

ggplot(data=continent_data, aes(x=Entity, y=affected_all_disasters)) +
    geom_bar(colour="black", fill="#DD8888", width=.8, stat="identity",position=position_dodge()) +
    coord_flip() +
    xlab("C") + 
    ylab("percentage of People affected") +
    labs(title = 'People affected by climate change disasters',
         subtitle = "Disasters: drought, heatwaves, flood, fog, wildfire, glacial lake",
         caption = "Number of people is calculated in percentage",
       ) + 
    labs(x = "") +
    theme_classic()
```

##### People affected due heatwaves in Asia

```{r message=FALSE}
# Checking the top 5 countries having affected_temperature due to disaster:
disaster_data_country_asia <- filter(disaster_data_country, (region %in% c(
                                                              "Asia")))
sorted = sort(disaster_data_country_asia$affected_temperature,decreasing = TRUE,index.return=TRUE)$ix

#Subseting Top20 countries by April 25th
top5 <- disaster_data_country_asia[sorted[1:10],]
top5 <- data.frame(Entity=disaster_data_country_asia$Entity[sorted[1:10]]) # construct a dataframe based on the top 5 countries
top5$Entity <- as.character(top5$Entity) # make the country names as character
#To plot:
top5_data <- dplyr::inner_join(disaster_data_country_asia,top5,by="Entity") #join two tables together 

#Barplot
top5_data$affected_temperature <- log (top5_data$affected_temperature)
p <- ggplot(top5_data, aes(x = reorder(Entity, +affected_temperature), y=affected_temperature, fill=sub.region)) + 
  geom_bar(stat = "identity") + 
  xlab(" ") +
  ylab("Number of people affected") +
  labs(title = 'Country affected by temperature',
       subtitle = "Number of people affected calculated in million"
       ) + 
  theme_classic() +
  coord_flip()
p
```

##### People affected due flood in Asia

```{r message=FALSE}
# Checking the top 5 countries having affected_flood due to disaster:
disaster_data_country_asia <- filter(disaster_data_country, (region %in% c(
                                                              "Asia")))
sorted = sort(disaster_data_country_asia$affected_flood,decreasing = TRUE,index.return=TRUE)$ix

#Subseting Top20 countries by April 25th
top5 <- disaster_data_country_asia[sorted[1:10],]
top5 <- data.frame(Entity=disaster_data_country_asia$Entity[sorted[1:10]]) # construct a dataframe based on the top 5 countries
top5$Entity <- as.character(top5$Entity) # make the country names as character
#To plot:
top5_data <- dplyr::inner_join(disaster_data_country_asia,top5,by="Entity") #join two tables together 
#length(unique(top5_data$Entity)) # Make sure the unique length is 5

#Barplot
top5_data$affected_flood <- log (top5_data$affected_flood)
p <- ggplot(top5_data, aes(x = reorder(Entity, +affected_flood), y=affected_flood, fill=sub.region)) + 
  geom_bar(stat = "identity") + 
  xlab(" ") +
  ylab("Number of people affected") +
  labs(title = 'Country affected by temperature',
       subtitle = "Number of people affected calculated in million"
       ) + 
  theme_classic() +
  coord_flip()
p
```

#### People died due to climate change disasters in all continents

```{r message=FALSE}
# No legend, since the information is redundant
# Add y axis units - TBD
#continent_data$affected_temperature <- log(continent_data$affected_temperature) 

continent_data$deaths_all_disasters= 100*(continent_data$deaths_all_disasters/sum(continent_data$deaths_all_disasters))

ggplot(data=continent_data, aes(x=Entity, y=deaths_all_disasters)) +
    geom_bar(colour="black", fill="#DD8888", width=.8, stat="identity",position=position_dodge()) +
    coord_flip() +
    xlab("C") + 
    ylab("percentage of People died") +
    labs(title = 'People affected by climate change disasters',
         subtitle = "Disasters: drought, temperature, flood, fog, wildfire, glacial lake",
         caption = "Number of people is calculated in percentage",
       ) + 
    labs(x = "") +
    theme_classic()
    #guides(fill=FALSE)

```

##### People died due climate change disasters in America

```{r message=FALSE}
# Checking the top 5 countries having deaths_all_disasters due to disaster:
disaster_data_country_americas <- filter(disaster_data_country, (region %in% c(
                                                              "Americas")))
sorted = sort(disaster_data_country_americas$deaths_all_disasters,decreasing = TRUE,index.return=TRUE)$ix

#Subseting Top20 countries by April 25th
top5 <- disaster_data_country_americas[sorted[1:10],]
top5 <- data.frame(Entity=disaster_data_country_americas$Entity[sorted[1:10]]) # construct a dataframe based on the top 5 countries
top5$Entity <- as.character(top5$Entity) # make the country names as character
#To plot:
top5_data <- dplyr::inner_join(disaster_data_country_americas,top5,by="Entity") #join two tables together 
#length(unique(top5_data$Entity)) # Make sure the unique length is 5

#Barplot
top5_data$deaths_all_disasters <- log (top5_data$deaths_all_disasters)
p <- ggplot(top5_data, aes(x = reorder(Entity, +deaths_all_disasters), y=deaths_all_disasters, fill=sub.region)) + 
  geom_bar(stat = "identity") + 
  xlab(" ") +
  ylab("Number of people affected") +
  labs(title = 'Country affected by temperature',
       subtitle = "Number of people affected calculated in million"
       ) + 
  theme_classic() +
  coord_flip()
p
```

##### People died due wildfire in America

```{r message=FALSE}
# Checking the top 5 countries having deaths_wildfire due to disaster:
disaster_data_country_americas <- filter(disaster_data_country, (region %in% c(
                                                              "Americas")))
sorted = sort(disaster_data_country_americas$deaths_wildfire,decreasing = TRUE,index.return=TRUE)$ix

#Subseting Top20 countries by April 25th
top10 <- disaster_data_country_americas[sorted[1:3],]
top10 <- data.frame(Entity=disaster_data_country_americas$Entity[sorted[1:3]]) # construct a dataframe based on the top 5 countries
top10$Entity <- as.character(top10$Entity) # make the country names as character
#To plot:
top10_data <- dplyr::inner_join(disaster_data_country_americas,top10,by="Entity") #join two tables together 
#length(unique(top5_data$Entity)) # Make sure the unique length is 5

#Barplot
top10_data$deaths_wildfire <- log (top10_data$deaths_wildfire)
p <- ggplot(top10_data, aes(x = reorder(Entity, +deaths_wildfire), y=deaths_wildfire, fill=sub.region)) + 
  geom_bar(stat = "identity") + 
  xlab(" ") +
  ylab("Number of people affected") +
  labs(title = 'Country affected by temperature',
       subtitle = "Number of people affected calculated in million"
       ) + 
  theme_classic() +
  coord_flip()
p
```

##### People died due flood in America

```{r message=FALSE}
# Checking the top 5 countries having deaths_flood due to disaster:
disaster_data_country_americas <- filter(disaster_data_country, (region %in% c(
                                                              "Americas")))
sorted = sort(disaster_data_country_americas$deaths_flood,decreasing = TRUE,index.return=TRUE)$ix

#Subseting Top20 countries by April 25th
top10 <- disaster_data_country_americas[sorted[1:10],]
top10 <- data.frame(Entity=disaster_data_country_americas$Entity[sorted[1:10]]) # construct a dataframe based on the top 5 countries
top10$Entity <- as.character(top10$Entity) # make the country names as character
#To plot:
top10_data <- dplyr::inner_join(disaster_data_country_americas,top10,by="Entity") #join two tables together 
#length(unique(top5_data$Entity)) # Make sure the unique length is 5

#Barplot
top10_data$deaths_flood <- log (top10_data$deaths_flood)
p <- ggplot(top10_data, aes(x = reorder(Entity, +deaths_flood), y=deaths_flood, fill=sub.region)) + 
  geom_bar(stat = "identity") + 
  xlab(" ") +
  ylab("Number of people affected") +
  labs(title = 'Country affected by temperature',
       subtitle = "Number of people affected calculated in million"
       ) + 
  theme_classic() +
  coord_flip()
p
```

#### People homeless due to all climate change disasters in all continents

```{r message=FALSE}
# homeless_all_disasters

continent_data$homeless_all_disasters= 100*(continent_data$homeless_all_disasters/sum(continent_data$homeless_all_disasters))

ggplot(data=continent_data, aes(x=Entity, y=homeless_all_disasters)) +
    geom_bar(colour="black", fill="#DD8888", width=.8, stat="identity",position=position_dodge()) +
    coord_flip() +
    ylab("percentage of People homeless") +
    labs(title = 'People death due to climate change disasters',
         subtitle = "Disasters: drought, heatwaves, flood, fog, wildfire, glacial lake",
         caption = "Number of people homeless is calculated in perentage",
       ) + 
    labs(x = "") +
    theme_classic()
```

##### People homeless due to all climate change disasters in Asia

```{r message=FALSE}
# Checking the top 5 countries having deaths_flood due to disaster:
disaster_data_country_asia_homeless <- filter(disaster_data_country, (region %in% c(
                                                              "Asia")))
sorted = sort(disaster_data_country_asia_homeless$homeless_all_disasters,decreasing = TRUE,index.return=TRUE)$ix

#Subseting Top20 countries by April 25th
top10 <- disaster_data_country_asia_homeless[sorted[1:10],]
top10 <- data.frame(Entity=disaster_data_country_asia_homeless$Entity[sorted[1:10]]) # construct a dataframe based on the top 5 countries
top10$Entity <- as.character(top10$Entity) # make the country names as character
#To plot:
top10_data <- dplyr::inner_join(disaster_data_country_asia_homeless,top10,by="Entity") #join two tables together 
#length(unique(top5_data$Entity)) # Make sure the unique length is 5

#Barplot
top10_data$homeless_all_disasters <- log (top10_data$homeless_all_disasters)
p <- ggplot(top10_data, aes(x = reorder(Entity, +homeless_all_disasters), y=homeless_all_disasters, fill=sub.region)) + 
  geom_bar(stat = "identity") + 
  xlab(" ") +
  ylab("Number of people affected") +
  labs(title = 'Country affected by temperature',
       subtitle = "Number of people affected calculated in million"
       ) + 
  theme_classic() +
  coord_flip()
p
```

##### People homeless due to flood in Asia

```{r message=FALSE}
# Checking the top 5 countries having homeless_flood due to disaster:
disaster_data_country_asia_homeless <- filter(disaster_data_country, (region %in% c(
                                                              "Asia")))
sorted = sort(disaster_data_country_asia_homeless$homeless_flood,decreasing = TRUE,index.return=TRUE)$ix

#Subseting Top20 countries by April 25th
top10 <- disaster_data_country_asia_homeless[sorted[1:10],]
top10 <- data.frame(Entity=disaster_data_country_asia_homeless$Entity[sorted[1:10]]) # construct a dataframe based on the top 5 countries
top10$Entity <- as.character(top10$Entity) # make the country names as character
#To plot:
top10_data <- dplyr::inner_join(disaster_data_country_asia_homeless,top10,by="Entity") #join two tables together 
#length(unique(top5_data$Entity)) # Make sure the unique length is 5

#Barplot
top10_data$homeless_flood <- log (top10_data$homeless_flood)
p <- ggplot(top10_data, aes(x = reorder(Entity, +homeless_flood), y=homeless_flood, fill=sub.region)) + 
  geom_bar(stat = "identity") + 
  xlab(" ") +
  ylab("Number of people affected") +
  labs(title = 'Country affected by temperature',
       subtitle = "Number of people affected calculated in million"
       ) + 
  theme_classic() +
  coord_flip()
p
```

#### People injured due to all climate change disasters in all continents

```{r message=FALSE}
# injured_all_disasters

continent_data$injured_all_disasters= 100*(continent_data$injured_all_disasters/sum(continent_data$injured_all_disasters))

ggplot(data=continent_data, aes(x=Entity, y=injured_all_disasters)) +
    geom_bar(colour="black", fill="#DD8888", width=.8, stat="identity",position=position_dodge()) +
    coord_flip() +
    ylab("percentage of total damages pct gdp all disaster") +
    labs(title = 'People death due to climate change disasters',
         subtitle = "Disasters: drought, temperature, flood, fog, wildfire, glacial lake",
         caption = "Number of people is calculated in perentage",
       ) + 
    labs(x = "") +
    theme_classic()
```

##### People injured  due to all climate change disasters in Asia

```{r message=FALSE}
# Checking the top 5 countries having injured_all_disasters due to disaster:
disaster_data_country_asia_injured <- filter(disaster_data_country, (region %in% c(
                                                              "Asia","North America")))
sorted = sort(disaster_data_country_asia_injured$injured_all_disasters,decreasing = TRUE,index.return=TRUE)$ix

#Subseting Top20 countries by April 25th
top10 <- disaster_data_country_asia_injured[sorted[1:10],]
top10 <- data.frame(Entity=disaster_data_country_asia_injured$Entity[sorted[1:10]]) # construct a dataframe based on the top 5 countries
top10$Entity <- as.character(top10$Entity) # make the country names as character
#To plot:
top10_data <- dplyr::inner_join(disaster_data_country_asia_injured,top10,by="Entity") #join two tables together 
#length(unique(top5_data$Entity)) # Make sure the unique length is 5

#Barplot
top10_data$injured_all_disasters <- log (top10_data$injured_all_disasters)
p <- ggplot(top10_data, aes(x = reorder(Entity, +injured_all_disasters), y=injured_all_disasters, fill=sub.region)) + 
  geom_bar(stat = "identity") + 
  xlab(" ") +
  ylab("Number of people affected") +
  labs(title = 'Country affected by temperature',
       subtitle = "Number of people affected calculated in million"
       ) + 
  theme_classic() +
  coord_flip()
p
```

##### People injured  due to heatwaves in Asia

```{r message=FALSE}
# Checking the top 5 countries having injured_temperature due to disaster:
disaster_data_country_asia_injured <- filter(disaster_data_country, (region %in% c(
                                                              "Asia","North America")))
sorted = sort(disaster_data_country_asia_injured$injured_temperature,decreasing = TRUE,index.return=TRUE)$ix

#Subseting Top20 countries by April 25th
top10 <- disaster_data_country_asia_injured[sorted[1:7],]
top10 <- data.frame(Entity=disaster_data_country_asia_injured$Entity[sorted[1:7]]) # construct a dataframe based on the top 5 countries
top10$Entity <- as.character(top10$Entity) # make the country names as character
#To plot:
top10_data <- dplyr::inner_join(disaster_data_country_asia_injured,top10,by="Entity") #join two tables together 
#length(unique(top5_data$Entity)) # Make sure the unique length is 5

#Barplot
top10_data$injured_temperature <- log (top10_data$injured_temperature)
p <- ggplot(top10_data, aes(x = reorder(Entity, +injured_temperature), y=injured_temperature, fill=sub.region)) + 
  geom_bar(stat = "identity") + 
  xlab(" ") +
  ylab("Number of people affected") +
  labs(title = 'Country affected by temperature',
       subtitle = "Number of people affected calculated in million"
       ) + 
  theme_classic() +
  coord_flip()
p
```

##### People injured  due to flood in Asia

```{r message=FALSE}
# Checking the top 5 countries having injured_flood due to disaster:
disaster_data_country_asia_injured <- filter(disaster_data_country, (region %in% c(
                                                              "Asia")))
sorted = sort(disaster_data_country_asia_injured$injured_flood,decreasing = TRUE,index.return=TRUE)$ix

#Subseting Top20 countries by April 25th
top10 <- disaster_data_country_asia_injured[sorted[1:10],]
top10 <- data.frame(Entity=disaster_data_country_asia_injured$Entity[sorted[1:10]]) # construct a dataframe based on the top 5 countries
top10$Entity <- as.character(top10$Entity) # make the country names as character
#To plot:
top10_data <- dplyr::inner_join(disaster_data_country_asia_injured,top10,by="Entity") #join two tables together 
#length(unique(top5_data$Entity)) # Make sure the unique length is 5

#Barplot
top10_data$injured_flood <- log (top10_data$injured_flood)
p <- ggplot(top10_data, aes(x = reorder(Entity, +injured_flood), y=injured_flood, fill=sub.region)) + 
  geom_bar(stat = "identity") + 
  xlab(" ") +
  ylab("Number of people affected") +
  labs(title = 'Country affected by temperature',
       subtitle = "Number of people affected calculated in million"
       ) + 
  theme_classic() +
  coord_flip()
p
```

#### total_damages_pct_gdp_all_disasters in all continents

```{r message=FALSE}
# total_damages_pct_gdp_all_disasters

continent_data$total_damages_pct_gdp_all_disasters= 100*(continent_data$total_damages_pct_gdp_all_disasters/sum(continent_data$total_damages_pct_gdp_all_disasters))

ggplot(data=continent_data, aes(x=Entity, y=total_damages_pct_gdp_all_disasters)) +
    geom_bar(colour="black", fill="#DD8888", width=.8, stat="identity",position=position_dodge()) +
    coord_flip() +
    ylab("percentage of total damages pct gdp all disaster") +
    labs(title = 'People death due to climate change disasters',
         subtitle = "Disasters: drought, temperature, flood, fog, wildfire, glacial lake",
         caption = "Number of people is calculated in perentage",
       ) + 
    labs(x = "") +
    theme_classic()
```

### Children Climate Risk Index

The CCRI generates new global evidence on the number of children who are currently exposed to climate and environmental hazards, shocks, and stresses through data analysis. Furthermore, the CCRI helps to understand and quantify the risks of climate and environmental shocks or stresses that lead to the erosion of development progress, the deepening of deprivation, and/or humanitarian situations affecting children or vulnerable households and groups. A composite index, the CCRI brings together geographical data by analyzing 1.) exposure to climate and environmental hazards, shocks and stresses; and 2.) child vulnerability.

The CCRI index looks to identify which nations or regions are at risk of humanitarian crises affecting children and child deprivation deepening as a result of their vulnerability to climate and environmental shocks or pressures. It also helps to recognize the underlying factors that may contribute to these risks.

```{r message=FALSE}
##Pre-processing
#Selecting only required columns from CC_ERI data for further analysis and visualization



cceri_data <- cceri_data %>% 
              select(REF_AREA,Geographic.area,Indicator,Value) %>%
              drop_na()

cceri_data <- cceri_data[!apply(is.na(cceri_data) | cceri_data == "", 1, any),]

cc_eri_data_new <- cceri_data %>%
                  pivot_wider(names_from = "Indicator",
                              values_from = "Value") %>% 
                  drop_na() 

#Removing space in the column names of the dataset
names(cc_eri_data_new) <- sub(" ", "_", names(cc_eri_data_new))

#Renaming the variables:
colnames(cc_eri_data_new)[1] <- "ISO_Code"
colnames(cc_eri_data_new)[4] <- "CCRI"
colnames(cc_eri_data_new)[6] <- "Child_health_nutrition"
colnames(cc_eri_data_new)[9] <- "Climate_environmental_shocks"
colnames(cc_eri_data_new)[21] <- "Soil_water_pollution"
colnames(cc_eri_data_new)[22] <- " Poverty_Inequality"
colnames(cc_eri_data_new)[23] <- "Social_protection_conomic_empowerment"
colnames(cc_eri_data_new)[25] <- "Vector_borne_diseases"
```

#### Climate Environmental Shocks

```{r message=FALSE}

cc_eri_data_new$Climate_environmental_shocks <- as.numeric(as.character(cc_eri_data_new$Climate_environmental_shocks))

#World map of country with heatwaves:
l <- list(color = toRGB("black"), width = 0.5) # light black boundaries

# specify map projection/options
g <- list(
  showframe = FALSE,
  showcoastlines = FALSE,
  projection = list(type = 'Mercator')
)
fig <- plot_geo(cc_eri_data_new)
fig <- fig %>% add_trace(
  z = ~Climate_environmental_shocks, color = ~Climate_environmental_shocks, colors = 'Purples',
  text = ~Geographic.area, locations = ~ISO_Code, marker = list(line = l)
)
fig <- fig %>% colorbar(title = 'Climate Environmental Shocks', tickprefix = '')
fig <- fig %>% layout(
  title = 'Climate Environmental Shocks - Worldwide',
  geo = g
)
fig
```

#### Child_vulnerability

```{r message=FALSE}

cc_eri_data_new$Child_vulnerability <- as.numeric(as.character(cc_eri_data_new$Child_vulnerability))
cc_eri_data_new <- cc_eri_data_new %>% drop_na() #removing na values in the dataset
#World map of country with heatwaves:
l <- list(color = toRGB("black"), width = 0.5) # light black boundaries
# specify map projection/options
g <- list(
  showframe = FALSE,
  showcoastlines = FALSE,
  projection = list(type = 'Mercator')
)
fig <- plot_geo(cc_eri_data_new)
fig <- fig %>% add_trace(
  z = ~Child_vulnerability, color = ~Child_vulnerability, colors = 'Blues',
  text = ~Geographic.area, locations = ~ISO_Code, marker = list(line = l)
)
fig <- fig %>% colorbar(title = 'Child Vulnerability', tickprefix = '')
fig <- fig %>% layout(
  title = 'Child Vulnerability - Worldwide',
  geo = g
)
fig
```

#### Children Climate Risk Index (CCRI) - Worldwide

```{r message=FALSE}
cc_eri_data_new$CCRI <- as.numeric(as.character(cc_eri_data_new$CCRI))

#World map of country with CCRI:
l <- list(color = toRGB("black"), width = 0.5) # light black boundaries
# specify map projection/options
g <- list(
  showframe = FALSE,
  showcoastlines = FALSE,
  projection = list(type = 'robinson')
)
fig <- plot_geo(cc_eri_data_new)
fig <- fig %>% add_trace(
  z = ~CCRI, color = ~CCRI, colors = 'Reds',
  text = ~Geographic.area, locations = ~ISO_Code, marker = list(line = l)
)
fig <- fig %>% colorbar(title = 'CCRI', tickprefix = '')
fig <- fig %>% layout(
  title = 'Children Climate Risk Index (CCRI) - Worldwide',
  geo = g
)
fig
```

## Conclusion
<p align='justify'>
The world is entering unprecedented era as climate change drives unprecedented global environmental, societal, and economic disruption. Exploring and analyzing the greenhouse gas emitters due to industrial revolution, while taking proper measures we can protect and support the society, especially the children.
</p>

## Data Source {.appendix}
<p align='justify'>
The data used for this study is extracted from *Our World in Data (OWID)*.
The data produced by is collected by UN, World Resources Institute , NASA and made available by Our World in Data. 
</p>
1. Emission levels with temperature <br>
	  Link : *< https://data.giss.nasa.gov/gistemp/  https://data.giss.nasa.gov/gistemp/tabledata_v4/T_AIRS/GLB.Ts+dSST.csv>* <br>
	  Latest Year : 2021 <br>
	  Observations :  <br>
	  Variables:  40 <br>
	  Last update: September 6, 2022<br>
	  Meta data:
	    - GISS Surface Temperature Analysis (GISTEMP v4)
	    - estimate of global surface temperature change
	    - Graphs and tables are updated around the middle of every month using current data files from NOAA GHCN v4(meteorological stations) and ERSST v5 (ocean areas)
	    - These updated files incorporate reports for the previous month and also late reports and corrections for earlier months.
      - Comparison with one-dimensional global climate models. 
	  
2. Natural disaster <br>
	  Link : *<https://raw.githubusercontent.com/owid/owid-datasets/master/datasets/Natural%20disasters%20(EMDAT%20–%20decadal)/Natural%20disasters%20(EMDAT%20–%20decadal).csv>* <br>
	  Latest Year : 2010 <br>
	  Observations: 1604 <br>
	  Variables: 164 <br>
	  Last update: 2021 <br>
	  Meta data:
	    - This data has been aggregated by Our World in Data by country and year based on the raw database of disasters published by EM-DAT, CRED / UCLouvain, Brussels, Belgium – www.emdat.be
	    - EM-DAT publishes comprehensive, global data on each individual disaster event – estimating the number of deaths; people affected; and economic damages, from UN reports; government records; expert opinion; and additional sources.
	    - Our World in Data have calculated annual aggregates, and decadal averages, for each country based on this raw event-by-event dataset.
Decadal figures are measured as the annual average over the subsequent ten-year period. This means figures for ‘1900’ represent the average from 1900 to 1909; ‘1910’ is the average from 1910 to 1919 etc.

3. Children’s Climate and Environment Risk Index (CCRI) <br>
    Metadata:
	  Link : *<https://github.com/owid/owid-datasets/tree/master/datasets/Global%20temperature%20anomaly%20-%20Met%20Office%20(HadCRUT4)>* <br>
	  Observations: 4075 <br>
	  Variables: 4 <br>
	  Last update: 2022 <br>
	  CCRI depends on two components:
    - Pillar 1 measures exposure to climate and environmental shocks and stresses. 
    - Pillar 2 captures child vulnerability. 
The data is updated regularly and most metrics are published on an annual basis.

## References {.unnumbered .appendix}

::: {}
James H. Stock, *Climate Change, Climate Policy, and Economic Growth, July 1, 2019* <https://heep.hks.harvard.edu/files/heep/files/dp_85_stock.pdf>

Luís Roberto Barroso, *TECHNOLOGICAL REVOLUTION, DEMOCRATIC RECESSION AND CLIMATE CHANGE: THE LIMITS OF LAW IN A CHANGING WORLD,2019*, https://carrcenter.hks.harvard.edu/files/cchr/files/ccdp_2019_009_technology_democracy.pdf
:::
